---
title: "Introduction to simulating data via regression"
author: "Fadhaa Ali"
date: "8^th^ December 2024"
output: html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to simulating data via regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(REGsimu)
```

## Overview

This package is to explain how applying lm model to data. 

## Workflow

Steps of fitting lm model to simulated data are given below:

1. Set the sample size n and the number of independent variables.

2. Set the parameters of the model $\beta_i$ and then generate $X_{.j}\sim N(n,0,1), where j=1,2,..,nv$

3. Calculate $y_i$ from $y_i=\beta_j X_{ij}+\epsilon_{i}$

4. format the generated data as data frame. Use the following function

```{r}
library(REGsimu)
data(rg_data)
head(rg_data)
```

Or you can generate the data by this code

```{r}
new_data<-rgsim(100,3)
head(new_data$data)
head(new_data$par)
```

5. Apply regress function to the generated data by

```{r}
model<-regress(new_data$data)
summary(model)
```

The output showing the estimated parameters and compared them to the original values


